### 2020-03-27 title.tex
update!!!!!
tweak

@@

\section*{Data availability}

All transcribed data and original reports used in this analysis are stored in a publicly available GitHub repository: \url{https://github.com/parksw3/COVID19-Korea}.
All code and traffic data are stored in a separate GitHub repository: \url{https://github.com/parksw3/Korea-analysis}.

>>>>

\section*{Keywords}

coronavirus disease, COVID-19, SARS-CoV-2, South Korea, social distancing

@@

\section*{Funding statement}

JD was supported from the Canadian Institutes of Health Research. The funders had no role in study design, data collection and analysis, decision to publish, or preparation of the manuscript.

\section*{Conflict of interest}

None declared.
